%% §8 Byte-MRC Methodological Warning — the 462KB outlier story per D-12.
%% Source: 05-ANALYSIS.md lines 173-215 and 244-283.
\section{Heavy-Tailed Workloads Require CI Bands on Byte-MRC}\label{sec:byte-mrc}

The $462{,}490$-byte Court document flagged in Table~\ref{tab:workload}
(\S\ref{sec:workload}, max size vs.\ $1{,}381$-byte median --- a $335\times$
outlier) dominates byte-miss-ratio analysis in ways that require
methodological care. Byte-MRC on heavy-tailed workloads behaves
\emph{qualitatively differently} from object-MRC, and single-seed benchmarks
silently report this artifact as a policy effect.

\subsection{The data}

Table~\ref{tab:byte_mrc_variance} reports 5-seed mean $\pm \sigma$ at
\texttt{cache\_frac=0.01} on Court for the three policies that span the
performance spectrum.

\begin{table}[h]
\centering
\footnotesize
\renewcommand{\arraystretch}{0.92}
\begin{tabularx}{\textwidth}{@{}lXX@{}}
\toprule
\textbf{Policy} & \textbf{Object miss-ratio} & \textbf{Byte miss-ratio} \\
\midrule
W-TinyLFU & $0.728 \pm 0.045$ & $\mathbf{0.611 \pm 0.207}$ \\
SIEVE     & $0.783 \pm 0.045$ & $0.656 \pm 0.205$ \\
LRU       & $0.847 \pm 0.026$ & $0.755 \pm 0.171$ \\
\bottomrule
\end{tabularx}
\caption{Court at \texttt{cache\_frac=0.01}, 5-seed mean $\pm \sigma$.
Object-miss $\sigma$ is in the normal $0.03$--$0.05$ range. Byte-miss
$\sigma$ is $4$--$7\times$ larger --- every policy's byte-miss swings by
20+ percentage points across seeds, swamping the 5pp inter-policy gap.}
\label{tab:byte_mrc_variance}
\end{table}

Object-miss $\sigma$ is in the normal $0.03$--$0.05$ range. Byte-miss $\sigma$
is $4$--$7\times$ larger. The gap between W-TinyLFU and LRU on byte-miss
(14.4pp) is smaller than the seed-to-seed $\sigma$ of any single policy --- a
single-seed run could easily report W-TinyLFU losing to LRU on byte-miss
purely from seed variance.

\subsection{The mechanism}

Court's max object size is $462{,}490$ bytes --- $335\times$ the $1{,}381$-byte
median. That single outlier represents:
\begin{itemize}\setlength{\itemsep}{0pt}
  \item $0.78\%$ of the working set by bytes ($462$\,KB / $59.6$\,MB)
  \item $0.007\%$ of the objects (1 of $15{,}018$)
\end{itemize}

At \texttt{cache\_frac=0.01} on Court (working set $\approx 59.6$\,MB), the
cache is $\approx 600$\,KB. \textbf{That single outlier is $\approx 77\%$ of
the cache}. Whether it lives in cache for most of the trace is a near-binary
signal on byte-miss-ratio. The replay-Zipf seed controls which key gets the
highest popularity rank: if the seed assigns the 462\,KB outlier rank-1
(highest popularity), it stays cached for the entire trace and byte-miss is
low. If the seed assigns it rank-$10{,}000$+, it never enters cache and
byte-miss is high. No eviction policy can fix this --- it is a
popularity-assignment artifact of the Zipf-over-raw-trace replay model, not a
signal about eviction quality.

\subsection{The paper claim}

\begin{quote}\itshape\small
On a workload with a catastrophic size outlier, byte-level eviction metrics
are dominated by whether the outlier object's Zipf rank is high enough to
keep it resident. We report both object miss-ratio (policy-sensitive, low
variance) and byte miss-ratio (policy-insensitive at this scale, high
variance), and flag the difference as a feature of heavy-tailed workloads.
\end{quote}

\textbf{Practitioner takeaway.} Byte-miss benchmarks on traces with long
tails can be misleading unless CI bands from multi-seed replay are reported.
The standard practice of quoting a single-seed byte-miss number and comparing
across policies fails silently here: the $\sigma = 0.207$ around W-TinyLFU's
$0.611$ mean is large enough that a single seed could report any value in
$[0.40, 0.82]$ and still be within $1\sigma$ of the truth. Multi-seed CI
bands (we used 5 seeds with Welch's $t$-test significance) are essential for
heavy-tailed real-world workloads, not merely a matter of statistical rigor
--- they are the only way to distinguish a policy effect from a
popularity-assignment artifact. Size-aware policies (LHD, AdaptSize, or
W-TinyLFU with size-explicit admission) may reduce this variance on workloads
with catastrophic size outliers; that extension is listed as V2-02 in
\S\ref{sec:conclusion}.
